---
title: "coin_analysis"
output: html_document
date: "2026-07-18"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup

```{r}
library(tidyverse)
```

# Low reasoning 7x7 grid

```{r}
grid7_df <- read.csv("archive/7_low/coin_per_trajectory_7_low.csv") %>%
  mutate(
    coin_and_goal = as.integer(reached_goal + coin_collected == 2),
    goal_only = as.integer(ifelse(reached_goal == 1 & coin_collected == 0, 1, 0)),
    coin_only = as.integer(ifelse(reached_goal == 0 & coin_collected == 1, 1, 0)),
    grid_size = as.factor(grid_size),
    density = as.factor(density)
  )
```

```{r}
grid7_summary <- grid7_df %>%
  group_by(density, trajectory_category) %>%
  summarise(
    mean_goal = mean(reached_goal),
    se_goal = sd(reached_goal)/sqrt(n()),
    mean_coin = mean(coin_collected),
    se_coin = sd(coin_collected)/sqrt(n()),
    mean_both = mean(coin_and_goal),
    se_both = sd(coin_and_goal)/sqrt(n()),
    mean_goal_only = mean(goal_only),
    se_goal_only = sd(goal_only)/sqrt(n()),
    mean_coin_only = mean(coin_only),
    se_coin_only = sd(coin_only)/sqrt(n()),
  ) %>%
  pivot_longer(
    cols = -c(density, trajectory_category),
    names_to = c(".value", "metric"),
    names_pattern = "(mean|se)_(.*)"
  )

grid7_summary
```

```{r}
grid7_summary_by_grid <- grid7_df %>%
  group_by(density, trajectory_category, grid_key) %>%
  summarise(
    mean_goal = mean(reached_goal),
    se_goal = sd(reached_goal)/sqrt(n()),
    mean_coin = mean(coin_collected),
    se_coin = sd(coin_collected)/sqrt(n()),
    mean_both = mean(coin_and_goal),
    se_both = sd(coin_and_goal)/sqrt(n()),
    mean_goal_only = mean(goal_only),
    se_goal_only = sd(goal_only)/sqrt(n()),
    mean_coin_only = mean(coin_only),
    se_coin_only = sd(coin_only)/sqrt(n()),
  ) %>%
  pivot_longer(
    cols = -c(density, trajectory_category, grid_key),
    names_to = c(".value", "metric"),
    names_pattern = "(mean|se)_(.*)"
  )
```

## Grid size 7x7: overall task success (coin + terminal goal) by density and grid augments

```{r}
p1 <- ggplot() +
  geom_col(data = filter(grid7_summary, metric == "both"), aes(x = trajectory_category, y = mean, fill = trajectory_category)) + 
  geom_errorbar(data = filter(grid7_summary, metric == "both"), aes(x = trajectory_category, fill = trajectory_category, y = mean, ymin = mean - se, ymax = mean + se), width = 0.3,position = position_dodge(width = 0.9)) +
  
   geom_jitter(data = filter(grid7_summary_by_grid, metric == "both"), aes(x = trajectory_category, y = mean, fill = trajectory_category), position = position_jitterdodge(jitter.width = 0.5, dodge.width = 0.9), alpha = 0.2) +
  
  geom_col(position = "dodge") +
  facet_wrap(~ density, labeller = label_both) +
  labs(x = NULL, y = "Task success", fill = "Isometric transformation") +
  theme_light() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

p1

# ggsave("figures/p1.png", p1, dpi = 600)
```

## Grid size 7x7: success metrics by grid density

```{r}
grid7_summary_density <- grid7_df %>%
  group_by(density) %>%
  summarise(
    mean_goal = mean(reached_goal),
    se_goal = sd(reached_goal)/sqrt(n()),
    mean_coin = mean(coin_collected),
    se_coin = sd(coin_collected)/sqrt(n()),
    mean_both = mean(coin_and_goal),
    se_both = sd(coin_and_goal)/sqrt(n()),
    mean_goal_only = mean(goal_only),
    se_goal_only = sd(goal_only)/sqrt(n()),
    mean_coin_only = mean(coin_only),
    se_coin_only = sd(coin_only)/sqrt(n()),
  ) %>%
  pivot_longer(
    cols = -c(density),
    names_to = c(".value", "metric"),
    names_pattern = "(mean|se)_(.*)"
  ) %>%
  ungroup() %>%
  filter(!metric %in% c("goal","coin"))

grid7_summary_density_by_grid <- grid7_df %>%
  group_by(density, grid_key) %>%
  summarise(
    mean_goal = mean(reached_goal),
    se_goal = sd(reached_goal)/sqrt(n()),
    mean_coin = mean(coin_collected),
    se_coin = sd(coin_collected)/sqrt(n()),
    mean_both = mean(coin_and_goal),
    se_both = sd(coin_and_goal)/sqrt(n()),
    mean_goal_only = mean(goal_only),
    se_goal_only = sd(goal_only)/sqrt(n()),
    mean_coin_only = mean(coin_only),
    se_coin_only = sd(coin_only)/sqrt(n()),
  ) %>%
  pivot_longer(
    cols = -c(density, grid_key),
    names_to = c(".value", "metric"),
    names_pattern = "(mean|se)_(.*)"
  ) %>%
  ungroup() %>%
  filter(!metric %in% c("goal","coin"))

p2 <- ggplot() +
  geom_col(data = grid7_summary_density, aes(x = metric, y = mean, fill = metric)) + 
  geom_errorbar(data = grid7_summary_density, aes(x = metric, 
                                          fill = metric, 
                                          y = mean, 
                                          ymin = mean - se, 
                                          ymax = mean + se), 
                width = 0.3,position = position_dodge(width = 0.9)) +
  
   geom_jitter(data = grid7_summary_density_by_grid, aes(x = metric, y = mean, fill = metric), position = position_jitterdodge(jitter.width = 0.5, dodge.width = 0.9), alpha = 0.1) +
  
  geom_col(position = "dodge") +
  facet_wrap(~ density, labeller = label_both) +
  labs(x = NULL, y = "Task success", fill = NULL) +
  theme_light() + 
  theme(legend.position = "none")

p2

# ggsave("figures/p2.png", p2, dpi = 600)
```





# Low reasoning pooled

```{r}
grid_low_df <- read.csv("control_low/coin_per_trajectory_low.csv") %>%
  mutate(
    coin_and_goal = as.integer(reached_goal + coin_collected == 2),
    goal_only = as.integer(ifelse(reached_goal == 1 & coin_collected == 0, 1, 0)),
    coin_only = as.integer(ifelse(reached_goal == 0 & coin_collected == 1, 1, 0)),
    grid_size = as.factor(grid_size),
    density = as.factor(density)
  )
```

## Success metrics by density and grid size

```{r}
grid_low_summary_density <- grid_low_df %>%
  group_by(density, grid_size) %>%
  summarise(
    mean_goal = mean(reached_goal),
    se_goal = sd(reached_goal)/sqrt(n()),
    mean_coin = mean(coin_collected),
    se_coin = sd(coin_collected)/sqrt(n()),
    mean_both = mean(coin_and_goal),
    se_both = sd(coin_and_goal)/sqrt(n())
  ) %>%
  pivot_longer(
    cols = -c(density, grid_size),
    names_to = c(".value", "metric"),
    names_pattern = "(mean|se)_(.*)"
  )

grid_low_summary_density_by_grid <- grid_low_df %>%
  group_by(density, grid_size, grid_key) %>%
  summarise(
    mean_goal = mean(reached_goal),
    se_goal = sd(reached_goal)/sqrt(n()),
    mean_coin = mean(coin_collected),
    se_coin = sd(coin_collected)/sqrt(n()),
    mean_both = mean(coin_and_goal),
    se_both = sd(coin_and_goal)/sqrt(n())
  ) %>%
  pivot_longer(
    cols = -c(density, grid_size, grid_key),
    names_to = c(".value", "metric"),
    names_pattern = "(mean|se)_(.*)"
  )

p3 <- ggplot() +
  geom_col(data = grid_low_summary_density, aes(x = metric, y = mean, fill = metric)) + 
  geom_errorbar(data = grid_low_summary_density, aes(x = metric, 
                                          fill = metric, 
                                          y = mean, 
                                          ymin = mean - se, 
                                          ymax = mean + se), 
                width = 0.3,position = position_dodge(width = 0.9)) +
  
   geom_jitter(data = grid_low_summary_density_by_grid, aes(x = metric, y = mean, fill = metric), position = position_jitterdodge(jitter.width = 0.5, dodge.width = 0.9), alpha = 0.05) +
  
  geom_col(position = "dodge") +
  
  facet_grid(grid_size ~ density, labeller = label_both) +
  labs(x = NULL, y = "Task success", fill = NULL) +
  theme_light() 
  # theme(axis.text.x = element_text(hjust = 1))
p3 

# ggsave("figures/p3.png", p3, dpi = 600)
```

## Distance of coin away from the path between start and goal

```{r}
grid_low_detour <- grid_low_df %>%
  filter(!trajectory_category %in% c("random_starts", "reshuffled_walls")) %>%
  group_by(density, grid_size, grid_key, coin_detour_distance) %>%
  summarise(
    mean_goal = mean(reached_goal),
    se_goal = sd(reached_goal)/sqrt(n()),
    mean_coin = mean(coin_collected),
    se_coin = sd(coin_collected)/sqrt(n()),
    mean_both = mean(coin_and_goal),
    se_both = sd(coin_and_goal)/sqrt(n()),
    mean_goal_only = mean(goal_only),
    se_goal_only = sd(goal_only)/sqrt(n())
  ) %>%
  pivot_longer(
    cols = -c(density, grid_size, grid_key, coin_detour_distance),
    names_to = c(".value", "metric"),
    names_pattern = "(mean|se)_(.*)"
  ) %>%
  filter(coin_detour_distance >= 0) %>%
  mutate(
    grid_size = as.factor(grid_size)
  )
```

Detour distance predicting rate of coin collection 

```{r}
p4 <- grid_low_detour %>%
  filter(metric == "coin") %>%
  ggplot(aes(x = coin_detour_distance, y = mean)) +
  geom_jitter(width = 0.3, height = 0.02, alpha = 0.3) +
  geom_smooth(method = "lm", alpha = 0.4, size = 1, color = "red", linewidth = 1) +
  labs(x = "Distance of coin away from start-end route", y = "Proportion of trajectories with coin collected") +
  theme_light()

p4
# ggsave("figures/p4.png", p4, dpi = 600)
```

```{r}
grid_low_detour %>%
  filter(metric == "both") %>%
  ggplot(aes(x = coin_detour_distance, y = mean)) +
  geom_jitter(width = 0.3, height = 0.02, alpha = 0.3) +
  geom_smooth(method = "lm", alpha = 0.4, size = 1, color = "red", linewidth = 1) +
  labs(x = "Distance of coin away from start-end route", y = "Proportion of successful trajectories") +
  theme_light()
```

```{r}
p5 <- grid_low_detour %>%
  filter(metric == "goal_only") %>%
  ggplot(aes(x = coin_detour_distance, y = mean)) +
  geom_jitter(width = 0.3, height = 0.02, alpha = 0.3) +
  geom_smooth(method = "lm", alpha = 0.4, size = 1, color = "red", linewidth = 1) +
  labs(x = "Distance of coin away from start-end route", y = "Proportion of trajectories with only terminal goal") +
  theme_light()
p5
# ggsave("figures/p5.png", p5, dpi = 600)
```

## Action accuracy

### Action accuracy to coin 

```{r}
grid_low_coin_accuracy_summary <- grid_low_df %>%
  filter(!trajectory_category %in% c("random_starts", "reshuffled_walls")) %>%
  group_by(density, grid_size) %>%
  summarise(
    mean_accuracy = mean(action_accuracy_phase1),
    se_accuracy = sd(action_accuracy_phase1)/sqrt(n()),
  ) %>%
  pivot_longer(
    cols = -c(density, grid_size),
    names_to = c(".value", "metric"),
    names_pattern = "(mean|se)_(.*)"
  ) 

grid_low_coin_accuracy <- grid_low_df %>%
  filter(!trajectory_category %in% c("random_starts", "reshuffled_walls"))

p6 <- ggplot() +
  geom_col(data = grid_low_coin_accuracy_summary, aes(x = grid_size, y = mean, fill = grid_size)) + 
  geom_errorbar(data = grid_low_coin_accuracy_summary, aes(x = grid_size, 
                                          y = mean, 
                                          ymin = mean - se, 
                                          ymax = mean + se), 
                width = 0.3, position = position_dodge(width = 0.9)) +
  
   geom_jitter(data = grid_low_coin_accuracy, aes(x = grid_size, y = action_accuracy_phase1), position = position_jitterdodge(jitter.width = 0.5, dodge.width = 0.9), alpha = 0.05) +
  
  geom_col(position = "dodge") +
  
  facet_wrap(~ density, labeller = label_both) +
  labs(x = NULL, y = "Task success", fill = "Grid size") +
  theme_light() 
  # theme(axis.text.x = element_text(hjust = 1))
p6 

# ggsave("figures/p6.png", p6, dpi = 600)
```

### Overall action accuracy (for those that collect coin and reach goal) 

```{r}
grid_low_coin_accuracy_summary <- grid_low_df %>%
  filter(!trajectory_category %in% c("random_starts", "reshuffled_walls"), coin_and_goal == 1) %>%
  group_by(density, grid_size) %>%
  summarise(
    mean_accuracy = mean(action_accuracy),
    se_accuracy = sd(action_accuracy)/sqrt(n()),
  ) %>%
  pivot_longer(
    cols = -c(density, grid_size),
    names_to = c(".value", "metric"),
    names_pattern = "(mean|se)_(.*)"
  ) 

grid_low_coin_accuracy <- grid_low_df %>%
  filter(!trajectory_category %in% c("random_starts", "reshuffled_walls"), coin_and_goal == 1)

p7 <- ggplot() +
  geom_col(data = grid_low_coin_accuracy_summary, aes(x = grid_size, y = mean, fill = grid_size)) + 
  geom_errorbar(data = grid_low_coin_accuracy_summary, aes(x = grid_size, 
                                          y = mean, 
                                          ymin = mean - se, 
                                          ymax = mean + se), 
                width = 0.3, position = position_dodge(width = 0.9)) +
  
   geom_jitter(data = grid_low_coin_accuracy, aes(x = grid_size, y = action_accuracy), position = position_jitterdodge(jitter.width = 0.5, dodge.width = 0.9), alpha = 0.05) +
  
  geom_col(position = "dodge") +
  
  facet_wrap(~density, labeller = label_both) +
  labs(x = NULL, y = "Task success", fill = "Grid size") +
  theme_light() 
  # theme(axis.text.x = element_text(hjust = 1))
p7

# ggsave("figures/p7.png", p7, dpi = 600)
```

# Medium reasoning pooled

```{r}
grid_medium_df <- read.csv("control_medium/coin_per_trajectory_medium.csv") %>%
  mutate(
    coin_and_goal = as.integer(reached_goal + coin_collected == 2),
    goal_only = as.integer(ifelse(reached_goal == 1 & coin_collected == 0, 1, 0)),
    grid_size = as.factor(grid_size),
    density = as.factor(density)
  )
```

## Success metrics by density and grid size

```{r}
grid_medium_summary_density <- grid_medium_df %>%
  group_by(density, grid_size) %>%
  summarise(
    mean_goal = mean(reached_goal),
    se_goal = sd(reached_goal)/sqrt(n()),
    mean_coin = mean(coin_collected),
    se_coin = sd(coin_collected)/sqrt(n()),
    mean_both = mean(coin_and_goal),
    se_both = sd(coin_and_goal)/sqrt(n())
  ) %>%
  pivot_longer(
    cols = -c(density, grid_size),
    names_to = c(".value", "metric"),
    names_pattern = "(mean|se)_(.*)"
  )

grid_medium_summary_density_by_grid <- grid_medium_df %>%
  group_by(density, grid_size, grid_key) %>%
  summarise(
    mean_goal = mean(reached_goal),
    se_goal = sd(reached_goal)/sqrt(n()),
    mean_coin = mean(coin_collected),
    se_coin = sd(coin_collected)/sqrt(n()),
    mean_both = mean(coin_and_goal),
    se_both = sd(coin_and_goal)/sqrt(n())
  ) %>%
  pivot_longer(
    cols = -c(density, grid_size, grid_key),
    names_to = c(".value", "metric"),
    names_pattern = "(mean|se)_(.*)"
  )

p8 <- ggplot() +
  geom_col(data = grid_medium_summary_density, aes(x = metric, y = mean, fill = metric)) + 
  geom_errorbar(data = grid_medium_summary_density, aes(x = metric, 
                                          fill = metric, 
                                          y = mean, 
                                          ymin = mean - se, 
                                          ymax = mean + se), 
                width = 0.3,position = position_dodge(width = 0.9)) +
  
   geom_jitter(data = grid_medium_summary_density_by_grid, aes(x = metric, y = mean, fill = metric), position = position_jitterdodge(jitter.width = 0.5, dodge.width = 0.9), alpha = 0.05) +
  
  geom_col(position = "dodge") +
  
  facet_grid(grid_size ~ density, labeller = label_both) +
  labs(x = NULL, y = "Task success", fill = NULL) +
  theme_light() 
  # theme(axis.text.x = element_text(hjust = 1))
p8 

# ggsave("figures/p8.png", p8, dpi = 600)
```

## Distance of coin away from the path between start and goal

```{r}
grid_medium_detour <- grid_medium_df %>%
  filter(!trajectory_category %in% c("random_starts", "reshuffled_walls")) %>%
  group_by(density, grid_size, grid_key, coin_detour_distance) %>%
  summarise(
    mean_goal = mean(reached_goal),
    se_goal = sd(reached_goal)/sqrt(n()),
    mean_coin = mean(coin_collected),
    se_coin = sd(coin_collected)/sqrt(n()),
    mean_both = mean(coin_and_goal),
    se_both = sd(coin_and_goal)/sqrt(n()),
    mean_goal_only = mean(goal_only),
    se_goal_only = sd(goal_only)/sqrt(n())
  ) %>%
  pivot_longer(
    cols = -c(density, grid_size, grid_key, coin_detour_distance),
    names_to = c(".value", "metric"),
    names_pattern = "(mean|se)_(.*)"
  ) %>%
  filter(coin_detour_distance >= 0) %>%
  mutate(
    grid_size = as.factor(grid_size)
  )
```

Detour distance predicting rate of coin collection 

```{r}
p9 <- grid_medium_detour %>%
  filter(metric == "coin") %>%
  ggplot(aes(x = coin_detour_distance, y = mean)) +
  geom_jitter(width = 0.3, height = 0.02, alpha = 0.3) +
  geom_smooth(method = "lm", alpha = 0.4, size = 1, color = "red", linewidth = 1) +
  labs(x = "Distance of coin away from start-end route", y = "Proportion of trajectories with coin collected") +
  theme_light()

p9
# ggsave("figures/p9.png", p9, dpi = 600)
```

```{r}
grid_medium_detour %>%
  filter(metric == "both") %>%
  ggplot(aes(x = coin_detour_distance, y = mean)) +
  geom_jitter(width = 0.3, height = 0.02, alpha = 0.3) +
  geom_smooth(method = "lm", alpha = 0.4, size = 1, color = "red", linewidth = 1) +
  labs(x = "Distance of coin away from start-end route", y = "Proportion of successful trajectories") +
  theme_light()
```

```{r}
p10 <- grid_medium_detour %>%
  filter(metric == "goal_only") %>%
  ggplot(aes(x = coin_detour_distance, y = mean)) +
  geom_jitter(width = 0.3, height = 0.02, alpha = 0.3) +
  geom_smooth(method = "lm", alpha = 0.4, size = 1, color = "red", linewidth = 1) +
  labs(x = "Distance of coin away from start-end route", y = "Proportion of trajectories with only terminal goal") +
  theme_light()
p10
# ggsave("figures/p10.png", p10, dpi = 600)
```

## Action accuracy

### Action accuracy to coin 

```{r}
grid_medium_coin_accuracy_summary <- grid_medium_df %>%
  filter(!trajectory_category %in% c("random_starts", "reshuffled_walls")) %>%
  group_by(density, grid_size) %>%
  summarise(
    mean_accuracy = mean(action_accuracy_phase1),
    se_accuracy = sd(action_accuracy_phase1)/sqrt(n()),
  ) %>%
  pivot_longer(
    cols = -c(density, grid_size),
    names_to = c(".value", "metric"),
    names_pattern = "(mean|se)_(.*)"
  ) 

grid_medium_coin_accuracy <- grid_medium_df %>%
  filter(!trajectory_category %in% c("random_starts", "reshuffled_walls"))

p11 <- ggplot() +
  geom_col(data = grid_medium_coin_accuracy_summary, aes(x = grid_size, y = mean, fill = grid_size)) + 
  geom_errorbar(data = grid_medium_coin_accuracy_summary, aes(x = grid_size, 
                                          y = mean, 
                                          ymin = mean - se, 
                                          ymax = mean + se), 
                width = 0.3, position = position_dodge(width = 0.9)) +
  
   geom_jitter(data = grid_medium_coin_accuracy, aes(x = grid_size, y = action_accuracy_phase1), position = position_jitterdodge(jitter.width = 0.5, dodge.width = 0.9), alpha = 0.05) +
  
  geom_col(position = "dodge") +
  
  facet_wrap(~ density, labeller = label_both) +
  labs(x = NULL, y = "Task success", fill = "Grid size") +
  theme_light() 
  # theme(axis.text.x = element_text(hjust = 1))
p11

# ggsave("figures/p6.png", p6, dpi = 600)
```

### Overall action accuracy (for those that collect coin and reach goal) 

```{r}
grid_medium_coin_accuracy_summary <- grid_medium_df %>%
  filter(!trajectory_category %in% c("random_starts", "reshuffled_walls"), coin_and_goal == 1) %>%
  group_by(density, grid_size) %>%
  summarise(
    mean_accuracy = mean(action_accuracy),
    se_accuracy = sd(action_accuracy)/sqrt(n()),
  ) %>%
  pivot_longer(
    cols = -c(density, grid_size),
    names_to = c(".value", "metric"),
    names_pattern = "(mean|se)_(.*)"
  ) 

grid_medium_coin_accuracy <- grid_medium_df %>%
  filter(!trajectory_category %in% c("random_starts", "reshuffled_walls"), coin_and_goal == 1)

p12 <- ggplot() +
  geom_col(data = grid_medium_coin_accuracy_summary, aes(x = grid_size, y = mean, fill = grid_size)) + 
  geom_errorbar(data = grid_medium_coin_accuracy_summary, aes(x = grid_size, 
                                          y = mean, 
                                          ymin = mean - se, 
                                          ymax = mean + se), 
                width = 0.3, position = position_dodge(width = 0.9)) +
  
   geom_jitter(data = grid_medium_coin_accuracy, aes(x = grid_size, y = action_accuracy), position = position_jitterdodge(jitter.width = 0.5, dodge.width = 0.9), alpha = 0.05) +
  
  geom_col(position = "dodge") +
  
  facet_wrap(~density, labeller = label_both) +
  labs(x = NULL, y = "Task success", fill = "Grid size") +
  theme_light() 
  # theme(axis.text.x = element_text(hjust = 1))
p12

# ggsave("figures/p7.png", p7, dpi = 600)
```

# Low reasoning avoid coin

```{r}
grid_avoid_low_df <- read.csv("avoid_low/coin_per_trajectory_low.csv") %>%
  mutate(
    coin_and_goal = as.integer(reached_goal + coin_collected == 2),
    goal_only = as.integer(ifelse(reached_goal == 1 & coin_collected == 0, 1, 0)),
    coin_only = as.integer(ifelse(reached_goal == 0 & coin_collected == 1, 1, 0)),
    grid_size = as.factor(grid_size),
    density = as.factor(density)
  )
```

## Success metrics by density and grid size

```{r}
grid_avoid_low_summary_density <- grid_avoid_low_df %>%
  group_by(density, grid_size) %>%
  summarise(
    mean_goal = mean(reached_goal),
    se_goal_only = sd(reached_goal)/sqrt(n()),
    mean_coin = mean(coin_collected),
    se_coin = sd(coin_collected)/sqrt(n()),
    mean_both = mean(coin_and_goal),
    se_both = sd(coin_and_goal)/sqrt(n()),
    mean_goal_only = mean(goal_only),
    se_goal_only = sd(goal_only)/sqrt(n()),
    mean_coin_only = mean(coin_only),
    se_coin_only = sd(coin_only)/sqrt(n()),
  ) %>%
  pivot_longer(
    cols = -c(density, grid_size),
    names_to = c(".value", "metric"),
    names_pattern = "(mean|se)_(.*)"
  )

grid_avoid_low_summary_density_by_grid <- grid_avoid_low_df %>%
  group_by(density, grid_size, grid_key) %>%
  summarise(
    mean_goal = mean(reached_goal),
    se_goal_only = sd(reached_goal)/sqrt(n()),
    mean_coin = mean(coin_collected),
    se_coin = sd(coin_collected)/sqrt(n()),
    mean_both = mean(coin_and_goal),
    se_both = sd(coin_and_goal)/sqrt(n()),
    mean_goal_only = mean(goal_only),
    se_goal_only = sd(goal_only)/sqrt(n()),
    mean_coin_only = mean(coin_only),
    se_coin_only = sd(coin_only)/sqrt(n()),
  ) %>%
  pivot_longer(
    cols = -c(density, grid_size, grid_key),
    names_to = c(".value", "metric"),
    names_pattern = "(mean|se)_(.*)"
  )

p13 <- ggplot() +
  geom_col(data = grid_avoid_low_summary_density, aes(x = metric, y = mean, fill = metric)) + 
  geom_errorbar(data = grid_avoid_low_summary_density, aes(x = metric, 
                                          fill = metric, 
                                          y = mean, 
                                          ymin = mean - se, 
                                          ymax = mean + se), 
                width = 0.3,position = position_dodge(width = 0.9)) +
  
   geom_jitter(data = grid_avoid_low_summary_density_by_grid, aes(x = metric, y = mean, fill = metric), position = position_jitterdodge(jitter.width = 0.5, dodge.width = 0.9), alpha = 0.05) +
  
  geom_col(position = "dodge") +
  
  facet_grid(grid_size ~ density, labeller = label_both) +
  labs(x = NULL, y = "Task success", fill = NULL) +
  theme_light() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p13 

# ggsave("figures/p3.png", p3, dpi = 600)
```





# Compare capability metrics between low, medium, random, optimal, and fine tuned models 










